Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-06 modeling-volunteer-computing-gecco.tex
Correciones de estilo y unas preguntillas a @JJ para el issue #2

The server program includes also additional logic for logging to
different files or services, routes to obtain information from the
server, such as the anonymized IPs that have participated in the
experiment, the ordinal number of the experiment that is being performed or the content of the chromosome pool, and code to serve the static pages
and the JavaScript/CSS
code also. The main changes to the code from the  the previous paper
\cite{arxiv:modeling} is, besides the inclusion of logging for a
better experiment analyis, the function that checks for the algorithm
termination condition and restarts the chromosome pool when
it does; it includes a configurable termination
condition that checks for the solution and empties the chromosome pool
and logs the end of the experiment. This allows us to run continuously
experiments without restarting the server by hand as we did in the
previous version.

@@

In this experiment we have used OpenShift (\url{http://openshift.com})
and Heroku (\url{http://heroku.com}) which are Platform as a Service products with a
free tier. It could be also be deployed, with small
or no modification, to other similar PaaS, maybe with a bit of adaptation. Any of them are
free up to a certain level of use and thus fulfill the requirement of
using free resources as a sustainable way of performing distributed
evolutionary compuation experiments \cite{Merelo2014,jj:idc:lowcost}.

@@

Having the pages and the server in the same domain allows to work in the
default Ajax mode, that does not allow cross-site requests. However,
these can also be enabled if needed so that the static pages and the
REST server can be hosted in different servers, allowing the genetic
algorithm code to {\em parasite} other pages.

In this case, every domain holds
a single experiment, there is no multi-tenancy of experiments, so its
management is quite simple. A different experiment would need to
deploy and start a server that serves different code and checks for
different termination conditions.

During and after the experiment, the data can be collected from one of
the logs: the server log file, data files (that cannot be used in
Heroku, for instance)  or from online logging services such as
Loggly (\url{http://loggly.com}), which is the one we are using. Loggly was chosen for its
easiness and support from the {\tt winston} logging library as well as
its graphing capabilities, shown in Figure \ref{fig:loggly}; however,
it is only free for a month, so a more sustainable alternative (read:
free and open source) will have to be sought in the future, after this paper is finished. Other online logging
services have a free tier that can be used for ever; however, its
support and graphing facilities were not so complete. Choosing a good logging
service for experiments in open science is, for us, an open issue but it is
outside the scope of this paper. It will have to be left for future
work.
%
\begin{figure*}[htb]
        \centering
        \includegraphics[width=0.9\linewidth]{img/loggly.png}
        \caption{Loggly dashboard showing the evolution of fitness for
        the last 10 minutes of an experiment.}\label{fig:loggly}
\end{figure*}

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}. 
will be analyzed in the next section.

>>>>

The server program includes also additional logic for logging to
different files or services, routes to obtain information from the
server, such as the anonymized IPs that have participated in the
experiment, the ordinal number of the experiment that is being performed or the content of the chromosome pool, and code to serve the static pages
and the JavaScript/CSS
code also. The main changes to the code from the  the previous paper
\cite{arxiv:modeling} is, besides the inclusion of logging for a
better experiment analyis, the function that checks for the algorithm
termination condition and restarts the chromosome pool when
it does; it includes a configurable termination
condition that checks for the solution and empties the chromosome pool
and logs the end of the experiment. This allows us to run continuously
experiments without restarting the server by hand as we did in the
previous version. %FERGU: es esta la única innovación al paper de Arxiv? A lo mejor no deberíamos mencionarlo ni usarlo como base

@@

In this experiment we have used OpenShift (\url{http://openshift.com})
and Heroku (\url{http://heroku.com}) which are Platform as a Service products with a
free tier. It could be also be deployed, with small
or no modification, to other similar PaaS, maybe with a bit of adaptation. Any of them are
free up to a certain level of use and thus fulfill the requirement of
using free resources as a sustainable way of performing distributed
evolutionary computation experiments \cite{Merelo2014,jj:idc:lowcost}.

@@

Having the pages and the server in the same domain allows to work in the
default Ajax mode, that does not allow cross-site requests. However, %FERGU: no todo el mundo sabe de Ajax y lo de cross-site, explícalo mejor
these can also be enabled if needed so that the static pages and the
REST server can be hosted in different servers, allowing the genetic
algorithm code to {\em parasite} other pages.

In this case, every domain holds %FERGU: si es referencia a lo de parasitar de arriba ponlo en el mismo párrafo, que parece que te refieres a lo "parasitar". Mejor "In this study"?
a single experiment, there is no multi-tenancy of experiments, so its
management is quite simple. A different experiment would need to
deploy and start a server that serves different code and checks for
different termination conditions.

During and after the experiment, the data can be collected from one of
the logs: the server log file, data files (that cannot be used in
Heroku, for instance)  or from online logging services such as
Loggly (\url{http://loggly.com}), which is the one we are using. Loggly was chosen for its
easiness and support from the {\tt winston} logging library as well as
its graphing capabilities, shown in Figure \ref{fig:loggly}; however,
it is only free for a month, so a more sustainable alternative (read:
free and open source) will have to be sought in the future, after this paper is finished. Other online logging %FERGU: esto de que "despues de que se termine el paper" no me mola mucho.
services have a free tier that can be used forever; however, its
support and graphing facilities were not so complete. Choosing a good logging
service for experiments in open science is, for us, an open issue, and it is
outside the scope of this paper, so it will have to be left for future
work.
%
\begin{figure*}[htb]
        \centering
        \includegraphics[width=0.9\linewidth]{img/loggly.png}
        \caption{Loggly dashboard showing the evolution of fitness for
        the last 10 minutes of an experiment.}\label{fig:loggly}
\end{figure*}

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}, and they 
will be analyzed in the next section.
